Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
final

Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}. For example, Mr. Kreider rewards children with small toys after they do well on a set of phrases. A reward system could be implemented where the currency is the honey from {\em Kimbee}. This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time. As this was only a quarter long project, this is left as future work.

@@

\subsection{Therapist Portal}

The {\em Therapist Portal}, see Figure \ref{fig:tech}, is the application the therapist will use to track his or her student's progress and listen to the student's audio recordings. It is written in Javascript using the jQuery library with Bootstrap for the design elements and look of the page.

\subsubsection{Connection to Child Audio}

\subsubsection{Playing of Audio}

@@

@@

Upon the completion of {\em Kimbee}, we met with Mr. Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}. His reaction was very positive. He found no real flaws with the application and expressed that it would be very useful for children and his work with the children he works with. He did have suggestions for the future that are listed below under section \ref{sec:future_work}. Unfortunately we did not have time to test our application with actual children and track the results but we are confident that {\em Kimbee} can be used in a real world setting.

@@

There are a few ways that we can expand on {\em Kimbee}. We plan on deploying the project for use in the Arlington Public School District to see how children respond and learn from {\em Kimbee} along with how experienced speech therapists use {\em Kimbee} to aid the therapy process. Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement. We can also enhance the child's experience by adding more mini-games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character.

@@

We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}.

>>>>

Many therapists currently use operant conditioning as a reward system \cite{Kreider:Intro}. For example, Mr. Kreider rewards children with small toys after they do well on a set of phrases. A reward system could be implemented where the currency is the honey from {\em Kimbee}. This would encourage students to play the game outside of the therapy sessions and motivate them to improve over time. As this was only a quarter long project, this is left as future work.\label{sec:currency}

@@

\subsection{Therapist Portal}
The {\em Therapist Portal}, see Figure \ref{fig:tech}, is the application the therapist will use to track his or her student's progress and listen to the student's audio recordings. It is written in Javascript using the jQuery library with Bootstrap for the design elements and look of the page.

\subsubsection{Connection to Child Audio}
When the portal is launched, the data for all of the children under the therapist is downloaded through a HTTP GET request to the central server. The data is returned as a JSON object a short amount of time after the page is loaded. The WAV files for each recording are not downloaded at this time because of the significant size of each file. Instead, each recording is lazy instantiated and only requested when the user clicks play. A unique ID represents each audio recording and if clicked, a request will be made to the central server for the WAV file of the recording. When this request returns with the audio, the data is injected into the DOM through a HTML audio tag and then played.

@@

Before any request for a recording is made, a cache is first checked to see if the recording is already on the client. If a cache miss occurs, then the request will be made. If a cache hit occurs, then the audio will be immediately injected into the DOM and played. This system allows the therapist to replay the same audio recording multiple times without having to make a significant number of requests. A system for pre-fetching was discussed but never implemented; we leave this as future work.

@@

Upon the completion of {\em Kimbee}, we met with Mr. Kreider in order to assess how a professional speech therapist would respond to the application and to see if he had any suggestions and improvements \cite{Kreider:Results}. His reaction was very positive. He found no real flaws with the application and expressed that it would be very useful for children to work with. He wants us to continue consulting and working with him in the future as he thought that {\em Kimbee} was very promising. He did have suggestions for the future that are listed below under section \ref{sec:future_work}. Unfortunately we did not have time to test our application with actual children and track the results but we are confident that {\em Kimbee} can be used in a real world setting.

@@

There are a few ways that we can expand on {\em Kimbee}. We plan on deploying the project for use in the Arlington Public School District to see how children respond and learn from {\em Kimbee} along with how experienced speech therapists use {\em Kimbee} to aid the therapy process. Along with this, we can also expand on the application itself by targeting speech sounds past the `R' and `W' sound replacement. We can also enhance the child's experience by adding more mini-games for the child to play and a token system for children to spend the honey they collect on aesthetics for the bee character. The token and currency system described at the end of section \ref{sec:currency} is also left as future work.

@@

We would like to thank Richard Kreider of the Arlington Public School District for meeting with us to discuss the viability and details of our project when it was in its developing stages and then again to discuss improvements when Kimbee was almost finished \cite{Kreider:Intro,Kreider:Results}. We would also like to thank Bruce Hemingway and the TA for helping us throughout the project with guidance and feedback.
